Verifying Demonstrations

### 2019-02-18 paper/system-model.tex
Fixes comment on identity systems in system model

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital certificate of her 
identity signed by \iac{CA}\footnote{%
  The \ac{CA} must be \emph{logically centralized} to prevent Sybil 
  attacks~\cite{SybilAttack}.
  See \cref{identity-limits} for a discussion on existing identity systems and 
  their limits.
}.

@@

We draw inspiration from the three traditionally desired properties for verifiability for voting:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we 
actually mean a personal device that can perform cryptographic operations and 
communicate with other local devices on Alice's behalf.
Furthermore, we assume that each participant has a digital certificate signed 
by \iac{CA}\footnote{%
  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
  do.
  The \ac{CA} can be centralized or decentralized, but as 
  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
    centralized} to prevent Sybil attacks.
  See \cref{identity-limits} for a discussion on existing identity systems and 
  their limits.
} that ensures a one-to-one mapping between an identity and a cryptographic 
key\footnote{%
  For every identity there exists at most one valid digital certificate.
}.

@@

We draw inspiration from the three traditionally desired properties for verifiability for voting:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)
